Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\ Through Sub-sampling and Reconstruction

### 2019-06-25 latex/afm-cs-main.tex
Minor text tweaks.
Change CS20NG to CS-20NG.
fix alha beta.

A simulation comparison between BPDN and BPVV is shown in
Fig.~\ref{fig:BPTV_demonstration}. The first column shows two raster
scans: the top is a 512 by 512 pixel image of a CS20NG grating (Ted Pella, USA) acquired
with an Agilent 5400 AFM and the bottom is a 256 by 256 pixel image of
DNA acquired with an Agilent 5500 AFM. For the CS20NG grating, we
sampled 15\% of the pixels with 50 pixel $\mu$-paths and 25\%
of the DNA image with 25 pixel long $\mu$-paths. The second columns
shows the full frame reconstructions using BPDN and the third columns
shows the result using BPVV (\textcolor{red}{with $\alpha = ??$ and $\beta = ??$}). The fourth column zooms in on the region
indicated by the red box in column one. Similarly, the fifth and six
columns show the detail of the reconstructions. The reconstruction
results show the artifacts apparent in the BPDN reconstruction are
largely mitigated using BPVV. Thus, in the remainder of the paper, we
focus exclusively on BPVV. These reconstructions wth BPVV took about
1.5 seconds for the DNA image and about 7 seconds for the
CS20NG (on a typical laptop computer).

@@

\section{Metrics}\label{sec:rdi}
In section~\ref{sec:results} we use three metrics to assess our
results. The first two seek to quantify image quality between two images.
Define a master image as $X$ and a reconstruction or corrupted version
as $Y$, with each having $s\times h=m$ pixels. Let $x=\textrm{vec}(X)$
and $y=\textrm{vec}(Y)$. Let $L$ be the dynamic range of the master
image $x$. Then the peak signal to noise ratio (PSNR) is given by
\begin{equation*}
  \text{PSNR}(x,y) = 10\log_{10}\frac{L^2}
  {\sqrt{\frac{1}{p^2} \sum_{i=1}^{m}( x_{i} - y_{i})^2 }}.
\end{equation*}

@@

\subsection{Comparison to full raster}\label{sec:cp_full}
We took scans of a Ted Pella CS20NG sample grating over an area with
holes on a 500 nm pitch. The holes are 20 nm deep. We scanned 5 micron
by 5 micron images using standard raster scans with 512 lines. For the
raster scans, we took scans at 1.0~Hz, 2.5~Hz, 5.0~Hz, 8.0~Hz and
10~Hz. We also took $\mu$-path scans with densities at 12.5\% and
25\% and reconstructed 512 by 512 pixel images. The CS scans were
taken with scan velocities equivalent to raster scan rates of 1.0~Hz,
2.0~Hz, 5.0~Hz and 8.0~Hz. For all CS scans, the $\mu$-paths are
$\scanD{muLenNM}$ nm long, which translates to $\scanD{muLenPix}$
pixels.

The free value of the deflection signal was approximately $-0.6$ volts
and we set the scanning reference to ${\rzs=\scanD{spScan}}$~volts
(for both raster and CS) and the withdraw reference to
${\rzup=\scanD{spMv}}$ volts. We set the $XY$-settle boundary to
$\pm \scanD{xyBoundaryMic}$ microns and required $\scanD{xySetSamps}$
samples within this boundary before moving to the $Z$-engage state.
The pre-scan length was $\scanD{preScanSamples}$ time steps. The
cantilever was a Budget Sensors ContAI-G, with a nominal length of 450
microns and spring constant of $k=0.2$~N/m.

% \SSData{G2}$& $g_6 = \SSData{G6}
The CS scans were reconstructed with BPVV. We set
${\alpha_v=\scanD{alpv}}$ and ${\alpha_h=\scanD{alph}}$. For the
raster scans, we discard data from the re-trace and divided the
remaining data for each scan line into 512 bins based on the \xc
sensor measurements. We then average the data in each bin to obtain
the value of one pixel. To remove the affects of piezo creep and
sample tilt, we then de-trend each individual line. De-trending each
line causes the flat portion between the holes in the horizontal
direction to appear at a different height than the flat portion
between holes in the vertical direction. To remove this effect, we
select a column of pixels on the left and right side of each image
that does not cross any holes (i.e., a vertical line through the flat
area), and register each scan line to a common height along these columns.
This step eases comparison with the CS scans and was inspired by a
feature in the AFM image processing toolbox \texttt{SPIW} \cite{spiw}.
The resulting images are shown in Fig.~\ref{fig:resultsF1_images}. The
color maps represent a range of $\pm$20 nm. The rows of pixels
indicated by the red lines are shown as cross sections
Fig.~\ref{fig:pixel_rows}.

>>>>

A simulation comparison between BPDN and BPVV is shown in
Fig.~\ref{fig:BPTV_demonstration}. The first column shows two raster
scans: the top is a 512 by 512 pixel image of a CS-20NG grating (Ted Pella, USA) acquired
with an Agilent 5400 AFM and the bottom is a 256 by 256 pixel image of
DNA acquired with an Agilent 5500 AFM. For the CS-20NG grating, we
sampled 15\% of the pixels with 50 pixel $\mu$-paths and 25\%
of the DNA image with 25 pixel long $\mu$-paths. The second columns
shows the full frame reconstructions using BPDN and the third columns
shows the result using BPVV (\textcolor{red}{with $\alpha = ??$ and $\beta = ??$}). The fourth column zooms in on the region
indicated by the red box in column one. Similarly, the fifth and six
columns show the detail of the reconstructions. The reconstruction
results show the artifacts apparent in the BPDN reconstruction are
largely mitigated using BPVV. Thus, in the remainder of the paper, we
focus exclusively on BPVV. These reconstructions wth BPVV took about
1.5 seconds for the DNA image and about 7 seconds for the
CS-20NG (on a typical laptop computer).

@@

\section{Metrics}\label{sec:rdi}
In section~\ref{sec:results} we use three metrics to assess our
results. The first two seek to quantify image quality between two images.
Define a master image as $X$ and a reconstruction or corrupted version
as $Y$, with each having $s\times h=m$ pixels. Let $x=\textrm{vec}(X)$
and $y=\textrm{vec}(Y)$. Let $L$ be the dynamic range of the master
image $x$. Then the peak signal to noise ratio (PSNR) is given by
\begin{equation*}
  \text{PSNR}(x,y) = 10\log_{10}\frac{L^2}
  {\sqrt{\frac{1}{m} \sum_{i=1}^{m}( x_{i} - y_{i})^2 }}.
\end{equation*}

@@

\subsection{Comparison to full raster}\label{sec:cp_full}
We took scans of a Ted Pella CS-20NG sample grating over an area with
holes on a 500 nm pitch. The holes are 20 nm deep. We scanned 5 micron
by 5 micron images using standard raster scans with 512 lines. For the
raster scans, we took scans at 1.0~Hz, 2.5~Hz, 5.0~Hz, 8.0~Hz and
10~Hz. We also took $\mu$-path scans with densities at 12.5\% and
25\% and reconstructed 512 by 512 pixel images. The CS scans were
taken with scan velocities equivalent to raster scan rates of 1.0~Hz,
2.0~Hz, 4.0~Hz, 5.0~Hz and 8.0~Hz. For all CS scans, the $\mu$-paths are
$\scanD{muLenNM}$ nm long, which translates to $\scanD{muLenPix}$
pixels.

The free value of the deflection signal was approximately $-0.6$ volts
and we set the scanning reference to ${\rzs=\scanD{spScan}}$~volts
(for both raster and CS) and the withdraw reference to
${\rzup=\scanD{spMv}}$ volts. We set the $XY$-settle boundary to
$\pm \scanD{xyBoundaryMic}$ microns and required $\scanD{xySetSamps}$
samples within this boundary before moving to the $Z$-engage state.
The pre-scan length was $\scanD{preScanSamples}$ time steps. The
cantilever was a Budget Sensors ContAI-G, with a nominal length of 450
microns and spring constant of $0.2$~N/m.

% \SSData{G2}$& $g_6 = \SSData{G6}
The CS scans were reconstructed with BPVV. We set
${\alpha=\scanD{alph}}$ and ${\beta=\scanD{alpv}}$. For the
raster scans, we discard data from the re-trace and divided the
remaining data for each scan line into 512 bins based on the \xc
sensor measurements. We then average the data in each bin to obtain
the value of one pixel. To remove the affects of piezo creep and
sample tilt, we then de-trend each individual line. De-trending each
line causes the flat portion between the holes in the horizontal
direction to appear at a different height than the flat portion
between holes in the vertical direction. To remove this effect, we
select a column of pixels on the left and right side of each image
that does not cross any holes (i.e., a vertical line through the flat
area), and register each scan line to a common height along these columns.
This step eases comparison with the CS scans and was inspired by a
feature in the AFM image processing toolbox \texttt{SPIW} \cite{spiw}.
The resulting images are shown in Fig.~\ref{fig:resultsF1_images}. The
color maps represent a range of $\pm$20 nm. The rows of pixels
indicated by the red lines are shown as cross sections
Fig.~\ref{fig:pixel_rows}.
